UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-20 paper/paper.tex
evaluation updates

\emph{/* Evaluation will go through each of Design stages and will perform necessary calculations. Some examples attached below. */}

\section{Methodology and setup description}
Tools:
Apache Spark, Google Data Trace, Workstation

\section{Uptime Based Distance From Intersection Points}

@@

Pricing: cc2.8xlarge
c_medium = upfront : 4146, perhour : 0.54 
c_heavy = upfront : 5000, perhour : 0.361

Pricing: m2.4xlarge
m_medium = upfront : 2604, perhour : 0.52 
m_heavy = upfront : 3156, perhour : 0.272

@@

\section{Recognize inefficiencies and suggest changes}

@@

\myparagraph{Squeeze-them-in suggestion strategy}

\myparagraph{Scheme 1}
total spare cpu = 3 697 171.44
total spare mem = 6 685 407.83
total distance: +3 500 037
total uptime = 8056601
cost per hour = \$7 519 848 / 8056601 = 0.93337723935938
new total cost = \$8 177 048 - \$657 200 = \$7 519 848
new cost per task = \$7 519 848 / 1234716525 = 0.00609034369245

new averages 
cpu per machine = 15972217.38/11651 = 1370.88 / 29 = 47.27
Avg mem usage per machine = 30676363.36/11651 = 2632.94/29 = 90.79
Avg tasks number per machine = 1234716525/11651 = 105975.15/29 = 3654.31

\myparagraph{Scheme 2}
total spare cpu = 3 694 240.56 
total spare mem = 6 682 956.59
total distance: +3 501 467
total uptime = 8053221

\myparagraph{New capacity configuration suggestion}

Input

c_name = cc2.8xlarge
c_light = "upfront" : "1762", "perhour" : "0.904" 
c_medium =  "upfront" : "4146", "perhour" : "0.54" 
c_heavy =  "upfront" : "5000", "perhour" : "0.361"

# values for size: m2.4xlarge region: us-east
# 1 year reservation
m_name = 'm2.4xlarge'
m_light =  "upfront" : "1088", "perhour" : "0.676" 
m_medium =  "upfront" : "2604", "perhour" : "0.52" 
m_heavy =  "upfront" : "3156", "perhour" : "0.272"

@@

@@

\newpage
\begin{thebibliography}{99}
\bibitem{spark} https://spark.apache.org
\bibitem{googleTrace} https://code.google.com/p/googleclusterdata
\bibitem{AWS:2014} http://forecastcloudy.net/2012/04/02/amazon-web-services-aws-ec2-pricing-data/ https://a0.awsstatic.com/pricing/1/deprecated/ec2/ri-light-linux.json https://a0.awsstatic.com/pricing/1/deprecated/ec2/ri-medium-linux.json https://a0.awsstatic.com/pricing/1/deprecated/ec2/ri-heavy-linux.json
\end{thebibliography}
\label{endpage}

>>>>

\section{Methodology}

Evaluation process can be splitted into four phases:
\begin{enumerate}
\item collection and transformation of pricing and usage data,
\item calculation of key indicators (\textit{cph, ip(scheme1, scheme2), KDI}) and cluster characteristics (\textit{total cost, performance averages}), 
\item suggestion of changes based on Algorithm~\ref{alg:squeeze-them-in} and~\ref{alg:new_configuration},
\item validation of positive correlation between \textit{KDI} and \textit{total cost} changes.
\end{enumerate}

\section{Setup description}

\myparagraph{Workstation}
Hardware - Intel Xeon 6-core x86\_64 2.4GHz, L3 cache 24MB, RAM 28GB. \\
Operating System - OS X Yosemite 10.10.2

\myparagraph{Platform}
Apache Spark 1.2.1\footnote{\url{https://spark.apache.org}} - an engine for large-scale data processing. All of map reduce jobs were written using Python API. Jobs were executed using standalone cluster mode with settings specified in Table~\ref{tab:spark_conf}. Job run times varied widely based on input data size and complexity of computations - from 20hs+ for transformations on 100G+ data to 1 minute aggregations on 100-200M input.

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l |}
    \hline
    \textbf{Setting name} & \textbf{Value} \\
    \hline
    spark.master & local \\
    \hline
    spark.driver.memory & 8G \\
    \hline
    spark.executor.memory & 20G \\
    \hline
    spark.default.parallelism & 500 \\
    \hline
    \end{tabular}
\end{center}
\label{tab:spark_conf}
\caption{Apache Spark standalone cluster configuration settings}
\end{table}

Settings were tweaked during computation mostly due to frequent Out Of Memory errors. Default driver and executor settings - 256M and 512M respectively - were not enough to handle the volume of input data. Further OOMs occurred during \textit{RRD.reduceByKey}\footnote{\url{https://spark.apache.org/docs/1.2.1/api/python/pyspark.html#pyspark.RDD.reduceByKey}} operations as it required to compute a fairly large hash map. Tweaks of \textit{spark.default.parallelism} setting worked the best as it enforced more granular input data chunking.

\section{Input data}

\myparagraph{Pricing data}

Amazon Web Services\footnote{\url{http://aws.amazon.com/}} offered variable pricing schemes based on uptime. Customer could choose an instance configuration and total cost would be calculated based on a number of hours of uptime per day.
The offering was splitted into three options:
\begin{enumerate}
\item light - low upfront and high per hour cost,
\item medium - medium upfront and medium per hour cost,
\item heavy - high upfront and low per hour cost.
\end{enumerate}

For evaluation purposes we choose two pricing schemes for two different VM configurations~\cite{AWS:2014}. Pricing details are specified in Table~\ref{tab:aws_pricing}

\begin{table}[h]
\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    \textbf{Name} & \textbf{Scheme} & \textbf{Upfront (\$)} & \textbf{Per hour (\$)} \\
    \hline
    cc2.8xlarge & light & 1762 & 0.904 \\
    \hline
    cc2.8xlarge & medium & 4146 & 0.54 \\
    \hline
    cc2.8xlarge & heavy & 5000 & 0.361 \\
    \hline
    m2.4xlarge & light & 1088 & 0.676 \\
    \hline
    m2.4xlarge & medium & 2604 & 0.52 \\
    \hline
    m2.4xlarge & heavy & 3156 & 0.272 \\
    \hline
    \end{tabular}
\end{center}
\label{tab:aws_pricing}
\caption{AWS pricing for reserved cc2.8xlarge and m2.4xlarge instances}
\end{table}

Pricing: m2.4xlarge
m_light =  upfront : 1088, perhour : 0.676
m_medium = upfront : 2604, perhour : 0.52 
m_heavy = upfront : 3156, perhour : 0.272

\myparagraph{Usage data}

\section{Calculate cph and ip}

\section{Transform initial Google data schema to below per day}

Schema after transformation (splitted per day)
        1,machine ID,INTEGER,YES
        2,uptime (how many hours machine is on),INTEGER,YES
        3,uptime based on summarized task time,INTEGER,YES
        4,total CPU usage,INTEGER,YES
        5,CPU capacity, INTEGER, YES
        6,total assigned memory usage,FLOAT,NO
        7,total maximum memory usage,FLOAT,NO
        8,MEMORY capacity,FLOAT,YES
        9,NUMBER of tasks per machine per day

\section{Calculate KDI and total cost on google trace data }

@@

@@

\myparagraph{Cluster SLO averages}

\section{Recognize inefficiencies with Threshold-based Report}

@@

\section{Squeeze-them-in suggestion strategy}

\myparagraph{Scheme 1}
total spare cpu = 3 697 171.44
total spare mem = 6 685 407.83
new KDI: +3 500 037
old KDI: +3 215 231
KDI change: +8.14\%
total uptime = 8056601
new total cost = \$8 177 048 - \$657 200 = \$7 519 848
cost change: -8.04\%
cost per hour = \$7 519 848 / 8056601 = 0.93337723935938
new cost per task = \$7 519 848 / 118869614 = 0.06326131419927

new averages 
cpu per machine = 15972217.38/11651 = 1370.88 / 29 = 47.27 +7.4\%
Avg mem usage per machine = 30676363.36/11651 = 2632.94/29 = 90.79 +7.41\%
Avg tasks number per machine = 1234716525/11651 = 105975.15/29 = +7.4\%

\myparagraph{Scheme 2}
total spare cpu = 3 694 240.56 
total spare mem = 6 682 956.59
new KDI: +5 913 933
old KDI: +5 431 137
KDI change: +8.16\%
total uptime = 8053221
new total cost = \$5 637 418 - \$532 840.76 = \$5 104 577.24
cost change: -9.45\%
cost per hour = \$5 104 577.24 / 8053221 = 0.63385535303204
new cost per task = \$5 104 577.24 / 119367988 = 0.04276336834964

new averages 
cpu per machine = 15972217.38/11646 = 1371.48 / 29 = 47.29 +7.44\%
Avg mem usage per machine = 30676363.36/11646 = 2634.07 / 29 = 90.83 +7.45\%
Avg tasks number per machine = 1234716525/11646 = 106020.65 / 29 = 3655.88 +7.45\%

\section{New capacity configuration suggestion}

@@

\section{Validate influence of suggestions and correlation with KDI}

@@

\newpage
\begin{thebibliography}{99}
\bibitem{spark} https://spark.apache.org
\bibitem{googleTrace} https://code.google.com/p/googleclusterdata
\bibitem{AWS:2014} Access: Apr 20th, 2015, https://a0.awsstatic.com/pricing/1/deprecated/ec2/ri-light-linux.json https://a0.awsstatic.com/pricing/1/deprecated/ec2/ri-medium-linux.json https://a0.awsstatic.com/pricing/1/deprecated/ec2/ri-heavy-linux.json
\end{thebibliography}
\label{endpage}
